A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise Limitations

Nevertheless, researches put some effort in improving this lower bound. In 2001,
Woelfel~\cite{WOELFEL01} published a new bound lower bound as well as a first 
nontrivial upper bound for the size of OBDDs representing $n$-bit integer
multiplication by utilizing the concept of \textit{universal hashing}. Therefore,
he utilized a universal family of hash functions to improve the exponential lower
bound on the OBDD-size of integer multiplication to
$2^{\lfloor\frac{n}{2}\rfloor}/96$. Moreover, Woelfel~\cite{WOELFEL01} proved
the upper bound for the OBDD-size of computing the middle bit of an $n$-bit
multiplication to be $7/3 \cdot 2^{\frac{4 \cdot n}{3}}$.

Nevertheless, all lower bounds for $n$-bit integer multiplication are exponential
in the number of nodes. Especially because of the high practical relevance of
$n$-bit integer multiplication this is one of the main drawbacks of the OBDD
representation~\cite{BRYANT86, BRYANT91, WOELFEL01}.

Another topic researchers put much effort into was the variable ordering problem.
Section~\ref{subsec:dynamic-variable-ordering} already described one possible
approach to this problem but there are many other approaches such as heuristics
and simulated annealing algorithms~\cite{BOLLIG96}.

Bollig and Wegener~\cite{BOLLIG96} studied the complexity of improving the
variable ordering. They investigated this problem by analyzing the following
problem: Given an OBDD representing $f$ and a size bound $s$. Does an OBDD exist,
also representing $f$ and respecting an arbitrary variable ordering, having at
most $s$ nodes? "Unfortunately", they were able to prove this problem to be 
NP-complete. Hence, improving the variable ordering of OBDDs is
NP-complete~\cite{BOLLIG96}. \tbr

>>>>

Nevertheless, researchers put some effort in improving this lower bound. In 2001,
Woelfel~\cite{WOELFEL01} published a new lower bound as well as a first nontrivial
upper bound for the size of OBDDs representing $n$-bit integer multiplication by
using the concept of \textit{universal hashing}. Therefore, he utilized a
universal family of hash functions to improve the exponential lower bound on the
OBDD-size of integer multiplication to $2^{\lfloor n/2 \rfloor}/96$.
Moreover, Woelfel~\cite{WOELFEL01} proved the upper bound for the OBDD-size of
computing the middle bit of an $n$-bit multiplication to be
$7/3 \cdot 2^{\left(4 \cdot n \right) / 3}$.

However, both lower bounds for $n$-bit integer multiplication are exponential
in the number of nodes. Especially because of the high practical relevance of
$n$-bit integer multiplication, this is one of the main drawbacks of the OBDD
representation~\cite{BRYANT86, BRYANT91, WOELFEL01}.

Another topic tackled by some research teams was the variable ordering problem.
Section~\ref{subsec:dynamic-variable-ordering} already outlined one possible
approach to this problem but there are many other approaches such as heuristics
and simulated annealing algorithms~\cite{BOLLIG96}.

Consequently, Bollig and Wegener~\cite{BOLLIG96} studied the complexity of
improving the variable ordering. They investigated this problem by analyzing the
following problem: Given an OBDD representing $f$ and a size bound $s$. Does an
OBDD exist, also representing $f$ and respecting an arbitrary variable ordering,
having at most $s$ nodes? "Unfortunately", they were able to prove this problem
to be NP-complete. Hence, improving the variable ordering of OBDDs is
NP-complete too~\cite{BOLLIG96}.
